Notes and other text

### 2023-04-15 doc/manuscript/translocation.qmd
Rework first three paragraphs of discussion

<!--# Title should be less than 135 characters -->

@@

We provide three lines of evidence that support evolutionary rescue as a primary mechanism of recovery in MYL frog systems.
First, our genomic analyses comparing naive and recovering MYL frog populations found notable differences in allele frequencies between adjacent Bd-naive and recovering <!--# Check on using "persistent" vs "recovering" vs "recovered" --> <!--# Roland response: Use "recovering" throughout -->populations, consistent with strong selection.
Importantly, some of the regions of the genome that showed signatures of selection are associated with known cellular and immunological mechanisms contributing to disease resistance in other species generally [@robledo2018; @robledo2020] and amphibians specifically [@rosenblum2008; @ellison2014] (for more information, see SI X).
For example, we identified a \~940kb region on contig 8 that shows evidence of selection in recovering populations and contains eight genes associated with either the MHC Class I or Class III regions<!--# Only Class I and II are mentioned in Results -->.
These results corroborate numerous previous studies linking MHC genes to Bd survival [e.g., @savage2011; @bataille2015].
Broadly, our genomic analyses imply that selection and rapid evolutionary change has contributed to survival in MYL frogs in the presence of Bd.
<!--# For brevity in the discussion, I tried to a pull a few key bullets out of Allie's text. Allie and Bree: Edit and expand as you see fit. -->

The second line of evidence that evolutionary rescue is a strong candidate mechanism for recovery is that repeated translocations and long-term monitoring of naturally recovered populations have demonstrated that resistant phenotypes are maintained beyond the natal environment in the presence of Bd (as reflected by the high year-one adult survival in 6 out of 12 translocated populations).
Moreover, resistance has a quantifiable phenotype in this system -- resistant, persisting populations have Bd infection intensities below the level known to cause significant host mortality [@vredenburg2010, @knapp2016].
Translocated populations maintain infection intensities below this threshold of infection intensity such that infection intensity is not a significant predictor of adult survival following translocations to new environments.
Finally, high adult survival in the presence of Bd persists into subsequent generations in non-natal environments, suggesting that resistance is heritable to some degree. Although previous studies have documented signatures of selection in hosts following disease-induced declines [@epstein2016, @gignoux-wolfsohn2021], our study is unique in that these three lines of evidence provide a strong case that evolved resistance begets population recovery in both natal and non-natal habitats, consistent with evolutionary rescue.

>>>>

<!--# Title should be less than 135 characters: Mark -->

@@

While previous studies have documented signatures of selection in hosts following disease-induced declines [@epstein2016, @gignoux-wolfsohn2021], a strong causal chain from selection, to an increase in host fitness in the presence of the pathogen, to subsequent host recoveries remains lacking in most wildlife-disease systems.
To robustly conclude that evolutionary rescue is the primary mechanism of host recovery, ideally evidence for each link in the causal chain should be provided.
Here, we provide evidence for each of these links.
First, our genomic analyses comparing naive and recovering MYL frog populations found notable differences in allele frequencies between adjacent Bd-naive and recovering populations, consistent with strong selection due to disease.
Importantly, some of the regions of the genome that showed signatures of selection are associated with known cellular and immunological mechanisms contributing to disease resistance in other species generally [@robledo2018; @robledo2020] and amphibians specifically [@rosenblum2008; @ellison2014; @grogan2018] (for more information, see SI X).
For example, we identified a \~940kb region on contig 8 that shows evidence of selection in recovering populations and contains eight genes associated with either the MHC Class I or Class III regions<!--# Only Class I and II are mentioned in Results. Mark: Check with Allie, the supporting information text says Class I and III -->.
These results corroborate numerous previous studies linking MHC genes to Bd survival [e.g., @savage2011; @bataille2015].
Broadly, our genomic analyses imply that selection and rapid evolutionary change has contributed to survival in MYL frogs in the presence of Bd.

Second, repeated translocations and long-term monitoring of naturally recovered populations demonstrate that fitness benefits of robust phenotypes are maintained beyond the natal environment in the presence of Bd.
Specifically, robust phenotypes in recovered populations have reduced infection intensities, below the level known to cause significant host mortality [@vredenburg2010, @knapp2016].
This phenotype persists following translocations to new environments --- translocated populations maintain infection intensities below this threshold and infection intensity is not a significant predictor of adult survival following translocation.
Moreover, high adult survival in the presence of Bd persists into subsequent generations in non-natal environments, suggesting that robust phenotypes are heritable to some degree.
Together, strong selection following disease-induced declines and heritable increases in fitness point to evolutionary rescue as an important driver of observed natural recoveries and host persistence in this system [@knapp2016].
A key advance of our study is that we take these exciting results a step further, leveraging natural evolutionary rescue and translocations to promote MYL frog recovery at the landscape scale.
